WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-04-27 article/Article.tex
change import callback signature and add import callback when calling auto_progress(True)
darcs-hash:20060427134155-2fc9d-914e20191066fcb77809554427aef26f25db3544.gz

@@

\verb$itk$ module can be very long to import. The \verb$itkConfig$ module define
a \verb$ImportCallback$ method which will be called when each sub module is
imported in the import process. \verb$ImportCallback$ can be customized to report the
progress status of the import process. It must be a function that can take
the name of the library being imported as a parameter. Here is an example of a very
basic callback function which display the name of the submodule being imported on
the standard error output.
\small \begin{verbatim}
import sys, itkConfig
def stderr_callback(name):
  print >> sys.stderr, name
itkConfig.ImportCallback = stderr_callback
import itk
\end{verbatim} \normalsize

@@

     \subsubsection{Creating wrapXXX.cmake files to wrap classes}

@@

ITK is a great library, with the drawback to be nearly unusable for prototyping,
and to have a poor support for other languages than C++. WrapITK address those
issue and finally give to ITK a good support for python. Java and Tcl, while
not as much tweaked than python part, also take benefit of the higher number of
wrapped classes, and of the increase of consistency in available types and names

>>>>

\verb$itk.auto_progress(True)$ also set an import callback which show the module name when
the module are imported.

@@

\verb$itk$ module can be very long to import. The \verb$itkConfig$ module define
a \verb$ImportCallback$ method which will be called when each sub module is
imported in the import process. \verb$ImportCallback$ can be customized to report the
progress status of the import process. It must be a function that can take
the name of the library being imported as a parameter. Here is an example of a very
basic callback function which display the name of the submodule being imported on
the standard error output.
\small \begin{verbatim}
import sys, itkConfig
def stderr_callback(name, progress):
  if progress == 0:
    print >> sys.stderr, "Loading %s..." % name,
  if progress == 1:
    print >> sys.stderr, "done"
itkConfig.ImportCallback = stderr_callback
import itk
\end{verbatim} \normalsize

\verb$progress$ take only the value $0$ and $1$, but may take values between $0$ and $1$
in the future.

@@

     \subsubsection{Creating wrap\_XXX.cmake files to wrap classes}

@@

ITK is a great library, with the drawback to be nearly unusable for prototyping,
and to have a poor support for other languages than C++. WrapITK address those
issue and finally give to ITK a good support for python. Java and Tcl, while
not as much tweaked than python part, also take benefit of the higher number of
wrapped classes, and of the increase of consistency in available types and names.
